Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-07-07 paper/ms.tex
update manuscript
Incorporate JH suggestions (part 1)
Co-authored-by: Joel Hartman <jhartman@astro.princeton.edu>

The Gaia imaging, reduced to its point-source catalog, provides
the initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
white circles in Figure~\ref{fig:scene}, overlaid on the DSS2 plates
and TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
not surprising that the field of \tn\ is crowded.  The resolved stars
that were of immediate concern for our false positive analysis were as
follows.
\begin{itemize}
  %
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  %
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3$'' west. The
    proper motions and parallax of this star imply it is comoving with
    \tn, though with a physical separation of $6.6\pm 0.1\,{\rm pc}$,
    it may not be bound.
  %
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4$'' north.  The
    Gaia parallax implies this is a giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9$'' from the target, but
too faint ($T=18.8$) to be the source of the observed transit signal.

@@

To assess the possibility that Star A is an eclipsing body, we created
light curves with a custom set of circular apertures with radii of
$2.1''$ and positions ranging from Star A (2.3$''$ west of \tn) to
2.3$''$ east of \tn.  We did not detect any variation of the transit
depth along this line of light curves, as would be expected if Star A
were the eclipse host.  The apertures east of \tn\ exclude over 90\%
of the flux from Star A.  The eclipse on Star A would therefore need
to be excessively deep to produce the observed eclipse depth.  We take
this as evidence that \tn\ is the source of the transit signal to
within $\approx2.0''$.

@@

We used the dedicated instrument pipeline to extract 1-dimensional,
wavelength calibrated spectra.  To measure radial velocities, \edit1{
Rafael TODO: what procedure was used?  What software packages?}.  The
velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:followup}.

\subsubsection{Veloce}
We acquired 34 spectra over 10 visits of \tn\ with using the Veloce
spectrograph, mounted on the AAT 4.0m telescope at Siding Spring
Observatory near Coonabarabran, Australia \citep{gilbert_veloce_2018}.
In Rosso form, Veloce provides coverage from 600--950$\,$nm at a
spectral resolution of $\approx 80{,}000$.

@@

\subsubsection{Transit Depth}
In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
binary host blend together, and reduce the ``true'' eclipse depth
$\delta_{\rm true}$ to the observed depth
$\delta_{\rm obs}$:
\begin{equation}
  \delta_{\rm obs}
  = 
  \delta_{\rm true} \frac{F_{\rm comp}}{F_{\rm total}},
\end{equation}
where the total system flux and the flux from only the companion
(``comp'') binary are labeled appropriately.  The requirement that the
eclipse is produced by stars and that $\delta_{\rm true} < 0.5$
translates to a bound on the faintest possible blended companion
system:
\begin{equation}
  \Delta m < -\frac{5}{2} \log_{10}
             \left( \frac{0.5}{\delta_{\rm obs}} \right).
\end{equation}
For \tn\ ($T=9.93$), this implies that any stellar companion invoked
to explain the transit depth must be brighter than $T=15.07$.  In
Figure~\ref{fig:fpscenario}, we set the spatial limit to 2$''$ based
on the precision at which we have localized the transits using
seeing-limited ground-based photometry.

@@

For a fixed secondary mass, we then asked whether any tertiary
companions existed for which the maximal expected eclipse depth could
have been larger than the observed depth.  In cases for which the
answer was yes, we could not rule out such hierarchical eclipsing
binary systems.  Conversely, we were ruled out systems for which at
fixed secondary mass no tertiary mass could enable eclipses of the
necessary depth (in ${\rm R_C}$-band, or in ${\rm B_J}$-band).  The
${\rm R_C}$-band limit corresponded to a secondary mass limit of $M_2
> 0.27 M_\odot$, and the ${\rm B_J}$-band corresponded to a stronger
limit of $M_2 > 0.70 M_\odot$.

@@

While the above constraints rule out HEBs, certain configurations of
BEB systems ({\it e.g.}, a background G2V+K6V binary) can produce blue
eclipses while remaining undetected along the line of sight.  Such
scenarios are constrained by the lack of an observed secondary
eclipse, and therefore require either eccentric orbits to avoid
secondary eclipses, or else a background twin binary system at double
the orbital period.  The only way to definitively rule out such
scenarios is to prove that the loss of light is from the target star,
for instance by detecting the Rossiter-McLaughlin effect during a
transit.

@@

While alternative approaches are available for simultaneously fitting
space and ground based photometry (in addition to radial velocimetry),
we opted for this approach because {\it i)} the radial velocimetry on
its own did not show evidence for a planetary signal, and {\it ii)} we
expected that this approach would provide the best measurement of the
planetary ephemeris, which is key for follow-up efforts.  The
assumption of a constant radius across all bandpasses was tested by
independently fitting each ground-based transit while letting the
planetary radius float (Section~\ref{subsec:colorphot}). The transit
depths did not significantly change between different bandpasses.

@@

\bibliographystyle{yahapj}                            
\bibliography{bibliography}

>>>>

The Gaia imaging, reduced to its point-source catalog, provides
the initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
white circles in Figure~\ref{fig:scene}, overlaid on the DSS2 plates
and TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
not surprising that the field of \tn\ is crowded.  The resolved stars
that were of immediate concern for our false positive analysis were as
follows.
\begin{itemize}
  %
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  %
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3''$ west. The
    proper motions and parallax of this star imply it is comoving with
    \tn and is separated from it by $6.6\pm 0.1\,{\rm pc}$.
    It is therefore likely an \cn\ member, but unlikely to be a bound
    binary compnaion.
  %
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4''$ north.  The
    Gaia parallax implies this is a giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9''$ from the target, but
too faint ($T=18.8$) to be the source of the observed transit signal.

@@

To assess the possibility that Star A is an eclipsing body, we created
light curves with a custom set of circular apertures with radii of
$2.1''$ and positions ranging from Star A (2.3$''$ west of \tn) to
2.3$''$ east of \tn.  We did not detect any variation of the transit
depth along this line of light curves. The apertures east of \tn\
exclude over 90\% of the flux from Star A.  The eclipse on Star A
would therefore need to have depth greater than unity to produce the
observed eclipse depth.  We take the lack of a transit depth variation
along these light curves as evidence that \tn\ is the source of the
transit signal to within $\approx2.0''$.  The lack of variation of
transit depth with aperture location is consistent with \tn\ being the
source of transits, because the uncertainty of the transit depth
measurements ($\approx 15\%$) is much greater than the maximum
dilution from Star A ($\approx 1\%$).

@@

We used the dedicated instrument pipeline to extract 1-dimensional,
wavelength calibrated spectra.  To measure radial velocities, \edit1{
Rafael/Paula TODO: what procedure was used?  What software packages?}.  The
velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:followup}.

\subsubsection{Veloce}
We acquired 34 spectra over 10 visits of \tn\ using the Veloce
spectrograph, mounted on the AAT 4.0m telescope at Siding Spring
Observatory near Coonabarabran, Australia \citep{gilbert_veloce_2018}.
In the ``Rosso'' instrument-mode, Veloce provides coverage from
600--950$\,$nm at a spectral resolution of $\approx 80{,}000$.

@@

\subsubsection{Transit Depth}
In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
binary host blend together, and reduce the ``true'' eclipse depth
$\delta_{\rm true}$ to the observed depth
$\delta_{\rm obs}$:
\begin{equation}
  \delta_{\rm obs}
  = 
  \delta_{\rm true} \frac{F_{\rm comp}}{F_{\rm total}},
\end{equation}
where the total system flux and the flux from only the companion
(``comp'') binary are labeled appropriately.  The requirement that the
eclipse is produced by fusion-powered stars and that $\delta_{\rm true} < 0.5$
translates to a bound on the faintest possible blended companion
system:
\begin{equation}
  \Delta m < -\frac{5}{2} \log_{10}
             \left( \frac{0.5}{\delta_{\rm obs}} \right).
\end{equation}
For \tn\ ($T=9.93$), this implies that any stellar companion invoked
to explain the transit depth must be brighter than $T=15.07$.  In
Figure~\ref{fig:fpscenario}, we set the spatial limit to 2$''$ based
on the precision at which we have localized the transits using
seeing-limited ground-based photometry.

@@

For a fixed secondary mass, we then asked whether any tertiary
companions existed for which the maximal expected eclipse depth could
have been larger than the observed depth.  In cases for which the
answer was yes, we could not rule out such hierarchical eclipsing
binary systems.  Conversely, we ruled out systems for which at
fixed secondary mass no tertiary mass could enable eclipses of the
necessary depth (in ${\rm R_C}$-band, or in ${\rm B_J}$-band).  The
${\rm R_C}$-band limit corresponded to a secondary mass limit of $M_2
> 0.27 M_\odot$, and the ${\rm B_J}$-band corresponded to a stronger
limit of $M_2 > 0.70 M_\odot$.

@@

While the above constraints rule out HEBs, certain configurations of
BEB systems ({\it e.g.}, a background G2V+K6V binary) can produce blue
eclipses while remaining undetected along the line of sight.  Such
scenarios are constrained by the lack of an observed secondary
eclipse, and therefore require either eccentric orbits to avoid
secondary eclipses, or else a background twin binary system at double
the orbital period.  The only way to definitively rule out such
scenarios is to prove that the loss of light is from the target star,
for instance by detecting the Rossiter-McLaughlin effect during a
transit, and confirming that the spectroscopic transit is consistent
with the photometric transit.

@@

While alternative approaches are available for simultaneously fitting
space and ground based photometry (in addition to radial velocimetry),
we opted for this approach because {\it i)} the radial velocimetry on
its own did not show evidence for a planetary signal, {\it ii)} we
expected that this approach would provide the best measurement of the
planetary ephemeris, which is key for follow-up efforts, and {\it
iii)} the assumption of identical limb-darkening across all bandpasses
seemed justified by the level of precision in the ground-based data.
The assumption of a constant radius across all bandpasses was tested
by independently fitting each ground-based transit while letting the
planetary radius float (Section~\ref{subsec:colorphot}). The transit
depths did not significantly change between different bandpasses.

@@

\clearpage
\bibliographystyle{yahapj}                            
\bibliography{bibliography}
